Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-26 qpip0.tex
Redefine zideal to be subnormalized too

\begin{theorem}
	\Ethan{Second part of main theorem this section}
	$(d_i, z_{good, i})\approx (d_i, z_{ideal, i})$
	\Ethan{Need to define $d_i$ here}
\end{theorem}
\begin{proof}

>>>>

Now define $z_{true}$ to be sampled from $D_x$... \Ethan{Or something like that},
and define $z_{ideal, i}=\tr(z_{good, i})z_{true}$.

\begin{theorem}
	\Ethan{Second part of main theorem this section}
	$z_{good, i}\approx z_{ideal, i}$
\end{theorem}
\begin{proof}
